Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 related-work.tex
cleaning up the discussion section
progressing slowly with the related work

Service monitoring data are increasingly being used and more across a variety of systems in which adaptability, flexibility, and environmental awareness are essential~\cite{pernici2016monitoring}. Monitoring can be performed on different types of system components and for several purposes. Service-oriented literature on the subject discussed the multitude of aspects related to monitoring for services; the interested reader is referred to ~\cite{ghezzi2007run},~\cite{metzger2010analytical}, or more recently~\cite{pernici2016monitoring} for an extensive presentation of the subject.

@@

>>>>

% testing... the performacen
% there is plenty of work on testing for finding fauls
% people: https://scholar.google.nl/citations?user=DWd972sAAAAJ&hl=en&oi=ao

A rich body of work exists that studies the evolution and maintenance of APIs from the perspective of source code evolution \cite{dig2006apis, hora2015developers, hora2015apiwave}. However, since service monitoring data are increasingly being used across a variety of systems in which adaptability, flexibility, and environmental awareness are essential~\cite{pernici2016monitoring} in our work we focus on the analysis of the runtime aspects of services. There has been also a large body of work on using dynamic analysis in order to support the reverse engineering of software systems\cite{Corn09-dynamic}: in our work we focus more on understanding the usage of a system or service from the perspective of its clients.

Monitoring can be performed on different types of system components and for several purposes. Service-oriented literature on the subject discussed the multitude of aspects related to monitoring for services; the interested reader is referred to ~\cite{ghezzi2007run},~\cite{metzger2010analytical}, or more recently~\cite{pernici2016monitoring} for an extensive presentation of the subject.

@@

Our 
- Lanza has done nice stuff for source code evolution patterns. we need more work on automatic detection of service / endpoint evolution patterns. as exemplified by the utilization evolution.
